\newpage
\addcontentsline{toc}{chapter}{Список использованных источников}
 	
\begin{thebibliography}{1}
	\bibitem{zigbee-certified-products} List of ZigBee certified products [Electronic resource] -- 2021. -- Mode of access: 
	https://csa-iot.org/csa-iot\_products/. -- Date of access: 13.12.2021.
	
	\bibitem{zigbee-alliance} ZigBee Alliance [Electronic resource] -- 2021. -- Mode of access: 
	https://csa-iot.org/all-solutions/zigbee/. -- Date of access: 13.12.2021.
	
	\bibitem{z-wave-certified-products} List of Z-Wave certified products [Electronic resource] -- 2021. -- Mode of access: 
	https://products.z-wavealliance.org. -- Date of access: 13.12.2021.
	
	\bibitem{z-wave-alliance} Z-Wave Alliance [Electronic resource] -- 2021. -- Mode of access: 
	 https://z-wavealliance.org/. -- Date of access: 13.12.2021.
	
	\bibitem{wi-fi-alliance} Wi-Fi Alliance [Electronic resource] -- 2021. -- Mode of access: 
	https://www.wi-fi.org/. -- Date of access: 13.12.2021.
	
	\bibitem{802.11i-2004} IEEE 802.11i, IEEE Computer Society -- 2004. -- Mode of access: 
	https://standards.ieee.org/ieee/802.11i/3127/
	
	\bibitem{zigbee-attacks} Ján Ďurech, Mária Franeková: Security attacks to ZigBee technology and their practical realization // 
	University of Žilina/Department of Control and Information Systems, Žilina, Slovakia -- 2014.
	-- Mode of access: https://www.cic.ipn.mx/~pescamilla/MS/papers\_2014/DurechandFranekova
	\newline 2014.pdf.   -- Date of access: 13.12.2021.
 	
 	\bibitem{cve-2017-13077} Common Vulnerabilities and Exposures: WPA2 reinstallation key [Electronic resource] -- 2021.
 	-- Mode of access: https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-13077.   -- Date of access: 13.12.2021.
 
	\bibitem{zigbee-security-analysis} Xueqi Fan, Fransisca Susan, William Long, Shangyan Li. Security Analysis of Zigbee. // 2017.
	-- Mode of access: https://courses.csail.mit.edu/6.857/2017/project/17.pdf. -- Date of access: 13.12.2021.
	
	\bibitem{formal-proof-of-z-wave-volnerability} Mario Lilli, Chiara Braghin, Elvinia Riccobene. Formal Proof of a Vulnerability in 
	Z-Wave IoT Protocol. // Computer Science Department, Universita degli Studi di Milano, Italy.
	-- Mode of access: https://www.scitepress.org/Papers/2021/105533/105533.pdf. -- Date of access: 13.12.2021.
	
	\bibitem{platformio} PlatformIO official documentation [Electronic resource] -- 2022. -- Mode of access:
	https://docs.platformio.org/en/latest/. -- Date of access: 12.05.2022.
	
	\bibitem{microej} MicroEJ Software Development Kit [Electronic resource] -- 2022. -- Mode of access:
	https://developer.microej.com/microej-sdk-software-development-kit/. -- Date of access: 12.05.2022.
	
	\bibitem{nanoFramework} .NET nanoFramework [Electronic resource] -- 2022. -- Mode of access:
	https://www.nanoframework.net/. -- Date of access: 12.05.2022.
	
	\bibitem{standard-77} СТБ 34.101.77-2020. Информационные технологии и безопасность. Криптографические 
	алгоритмы на основе sponge-функции -- Введ. 2020 -- Минск: БелГИСС, 2020.
 	
\end{thebibliography}