\newpage
 	
	 \begin{thebibliography}{1}
	 	\addcontentsline{toc}{chapter}{Список использованных источников}
	 	
	 	\bibitem{zigbee-certified-products} List of ZigBee certified products. -Mode of access: 
	 	\newline https://zigbeealliance.org/product\_type/certified\_product/. -Date of access: 13.12.2021.
	 	
	 	\bibitem{zigbee-alliance} ZigBee Alliance. -Mode of access: 
	 	\newline https://zigbeealliance.org/solution/zigbee/. -Date of access: 13.12.2021.
	 	
	 	\bibitem{z-wave-certified-products} List of Z-Wave certified products. -Mode of access: 
	 	\newline https://products.z-wavealliance.org. -Date of access: 13.12.2021.
	 	
	 	\bibitem{z-wave-alliance} Z-Wave Alliance. -Mode of access: 
	 	\newline https://z-wavealliance.org/. -Date of access: 13.12.2021.
	 	
	 	\bibitem{wi-fi-alliance} Wi-Fi Alliance. -Mode of access: 
	 	\newline https://www.wi-fi.org/. -Date of access: 13.12.2021.
	 	
	 	\bibitem{802.11i-2004} IEEE 802.11i, IEEE Computer Society, 2004.
	 	
	 	\bibitem{zigbee-attacks} Ján Ďurech, Mária Franeková: Security attacks to ZigBee technology and their practical realization. 
	 	SAMI,  Herl’any, Slovakia, 2014.
	 	
	 	\bibitem{cve-2017-13077} Common Vulnerabilities and Exposures: WPA2 reinstallation key. -Mode of access: 
	    https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-13077.  \newline -Date of access: 13.12.2021.
	    
	    \bibitem{zigbee-security-analysis} Security Analysis of Zigbee. -Mode of access: \newline
	    https://courses.csail.mit.edu/6.857/2017/project/17.pdf. -Date of access: 20.03.2022.
	    
	    \bibitem{formal-proof-of-z-wave-volnerability} Formal Proof of a Vulnerability in Z-Wave IoT Protocol. -Mode of access: \newline
	    https://www.scitepress.org/Papers/2021/105533/105533.pdf. -Date of access: 21.03.2022.
	    
	    \bibitem{platformio} PlatformIO official documentation. -Mode of access: \newline
	    https://docs.platformio.org/en/latest/. -Date of access: 12.05.2022.
	    
	    \bibitem{microej} MicroEJ Software Development Kit. -Mode of access: \newline
	    https://developer.microej.com/microej-sdk-software-development-kit/. -Date of access: 12.05.2022.
	    
	    \bibitem{nanoFramework} .NET nanoFramework. -Mode of access: \newline
	    https://www.nanoframework.net/. -Date of access: 12.05.2022.
	    
	    \bibitem{standard-77} Информационные технологии и безопасность. Криптографические алгоритмы 
	    на основе sponge-функции $/$ СТБ 34.101.77-2020.
	 	
	 \end{thebibliography}